Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-20 article.tex

Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
for correlation, GTE and partial correlation on the \textit{normal-2}
dataset. The partial correlation outperforms other state-of-the-art methods
by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
AUROC.

Two reasons might explain such differences: (i) among
those methods only the partial correlation makes the distinction between
direct and indirect connections, (ii) the simulated network from the
\citep{stetter2012model} generator could be reduced to a linear model after
pre-processing. Those results is obviously generalized over the other
datasets see Appendix \textcolor{red}{REF}.

\begin{figure}[bth]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{The weighted average of partial correlation matrix, winning approach
         of the challenge, yields better than AUROC and AUPRC than all
         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         averaging method, partial correlation used filer $f_1$).}
\label{fig:curves}
\end{figure}

>>>>

Figure \ref{fig:curves} shows the ROC curve  and precision-recall curve
for correlation, GTE and partial correlation on the \textit{normal-2}
dataset. The partial correlation outperforms other state-of-the-art methods
by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
AUROC. Two reasons might explain such differences: (i) among
those methods only the partial correlation makes the distinction between
direct and indirect connections, (ii) the simulated network from the
\citep{stetter2012model} generator or the neural network in general could be
reduced to a linear model after pre-processing. Those results is obviously
generalized over the other datasets see Appendix \textcolor{red}{REF}.

\begin{figure}[bth]
\centering
\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{The weighted average of partial correlation matrix, winning approach
         of the challenge, yields better than AUROC and AUPRC than all
         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         averaged partial correlation method, partial correlation used
         filter $f_1$).}
\label{fig:curves}
\end{figure}
